---
title: "NBA Score Growth and 3 Point Analysis"
author: "Veer Patel"
---

The NBA score has grew in past years a big reason is due to the change in field goal percentage and ratios in three point shooting. The data for this analysis was sourced from a comprehensive NBA dataset on Kaggle. The dataset includes game statistics and player details, which helped gather an in-depth analysis of score growth and 3-point shooting trends over the years. Data cleaning involved filtering relevant seasons and ensuring consistent, thorough, and true formats for variables. Key variables such as game scores and 3-point attempts were measured in points and attempts per game to help uncover trends and correlations. I had loaded the dataset "path/to/nba_dataset.csv" as nba data, and used nba_cleaned to clean unnecessary data. In today's game of basketball, athletes are shooting more threes and making more threes than in the past, by a lot. 

```{r setup, message = false, warning = false}
library(dplyr)
library(ggplot2)
library(readr)
```

```{r}
nba_data <- read_csv("nba_data.csv")
nba_cleaned <- nba_data|>
  filter(season >= 2000) |>
  mutate(
    game_date = as.Date(game_date, format="%Y-%m-%d"),
    points_per_game = total_points / games_played,
    three_pointers_per_game = three_pointers_made / games_played
  )
summary(nba_cleaned)
ggplot(nba_cleaned, aes(x = season)) +
  geom_line(aes(y = points_per_game, color = "Points Per Game")) +
  geom_line(aes(y = three_pointers_per_game, color = "3-Pointers Per Game")) +
  labs(title = "NBA Score Growth and 3-Pointers Analysis",
       x = "Season",
       y = "Average per Game") +
  scale_color_manual(values = c("Points Per Game" = "blue", "3-Pointers Per Game" = "red"))
```

 

